---
title: 'The Urban Matrix, Arthropods, and Community Garden Yield: Code for Analyses'
author: "Asia Kaiser"
date: "April 2023"
output:
  pdf_document: default
  html_document: default
---

##### Loading packages
*Install packages before loading*

```{r, include=FALSE}
library(vegan)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lme4)
library(lmerTest)
library(nlme)
library(lattice)
library(iNEXT)
library(spatstat) 
library(scales)
library(ggthemes)
library(report)
library(AER)
library(ggiraphExtra)
library(piecewiseSEM)
library(mvabund)
library(ggpubr)
library(geosphere)
library(multcompView)
library(multcomp)
```

##### Reading in the dataframe

```{r}
rm(list=ls()) #clear global environment

GGALL <-read.csv("GGALL.csv")
head(GGALL)

GGAugust <-read.csv("GGAugust.csv")

GGsite <-read.csv("GGsite.csv")
summary(GGsite)

BeeNMDSinput <-read.csv("BeeNMDSinput.csv")
BeeNMDSinput <- t(BeeNMDSinput)
BeeNMDSinput <-BeeNMDSinput[-1,]

GGspecieWide.ALL <-read.csv("GGspecieWide.ALL.csv")
```

## Data Exploration

##### Descriptive statistics
```{r}
#Site imperviousness and wealth mean and sd
mean(GGsite$imp200m)
sd(GGsite$imp200m)
mean(GGsite$wealth_index_2022)
sd(GGsite$wealth_index_2022)
```


##### Preliminary data visualization
```{r}
#Histogram of Arthropod Abundances
hist(GGsite$n.obs,
     main = "Histogram of Arthropod Abundance",
     xlab = "Abundance")

hist(GGAugust$mass_g)
shapiro.test(GGAugust$mass_g)
shapiro.test(GGAugust$proportion_herbivory)

#Herbivory data
c1<- ggplot(GGAugust, aes(x = proportion_herbivory, y = reorder(plant_code, proportion_herbivory))) +
  geom_point(size = 3) + 
  theme(
    axis.text.y=element_blank(),
      axis.ticks.y=element_blank(),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
  ylab("Plant code")+
  xlab("% Herbivory")

#Pepper Fruit data
c2 <- ggplot(GGAugust, aes(x = mass_g, y = reorder(plant_code, mass_g))) +
  geom_point(size = 3) + 
  theme(
    axis.text.y=element_blank(),
      axis.ticks.y=element_blank(),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
  ylab("Plant code")+
  xlab("Mass (g)")

#Pepper fruit with log transformation
GGAugust$log_mass_g <-log(GGAugust$mass_g)
c3 <-ggplot(GGAugust, aes(x = log_mass_g, y = reorder(plant_code, log_mass_g))) +
  geom_point(size = 3) + 
  theme(
    axis.text.y=element_blank(),
      axis.ticks.y=element_blank(),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
  ylab("Plant code")+
  xlab("Log mass (g)")

#Herbivory data with log transformation
GGAugust$log_herbivory <-log(GGAugust$proportion_herbivory)

c4 <-ggplot(GGAugust, aes(x = log_herbivory, y = reorder(plant_code, log_herbivory))) +
  geom_point(size = 3)+ 
  theme(
    axis.text.y=element_blank(),
      axis.ticks.y=element_blank(),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
  ylab("Plant code")+
  xlab("Log % herbivory")

supp1panelfig <-ggarrange(c1,c4,c2,c3)
ggsave("supp1.png", supp1panelfig, width = 12, height = 8, units = "in")

sum(GGsite$n.obs.herb)
sum(GGsite$n.obs.pred)
sum(GGsite$n.obs.pol)
```

### Tests of Normality for Data

```{r}
shapiro.test(GGAugust$log_mass_g) #normal
shapiro.test(GGAugust$log_herbivory) #normal

shapiro.test(GGALL$n.obs) #not normal
shapiro.test(GGsite$n.obs.pol) # not normal
shapiro.test(GGsite$bee.simpson) #not normal

GGsite$log_bee.simpson <-log(GGsite$bee.simpson)
GGAugust$log_bee.simpson <-log(GGAugust$bee.simpson.x)
shapiro.test(GGsite$log_bee.simpson)
hist(GGsite$log_bee.simpson)
```


## Analyses

### Question 1: How do urbanization (impervious surface) and socioeconomic conditions surrounding garden site impact insect abundance?

Look at autocorrelation between predictor variables

```{r}
cor.test(GGsite$imp200m,GGsite$scaled_wealth_index_2022)
#Not a significant correlation
```

#Running Negative Binomial to Address Overdispersion

```{r}
insects.glm.2 <-glmer.nb(n.obs ~ imp200m+scaled_wealth_index_2022 + (1|month), data = GGsite)
summary(insects.glm.2)

backtransformed_q1 <- data.frame (predictor= c("imp1km", "wealthindex"),
                  anti_log_coef = c(exp(-0.06255),exp(0.05613)),
                  anti_log_lowCI = c(exp(-0.06255-0.02599),exp(0.05613-0.09941)),
                  anti_log_highCI = c(exp(-0.06255+0.02599),exp(0.05613+0.09941)))

plot(insects.glm.2)
qqnorm(GGsite$n.obs, pch = 1, frame = FALSE)
qqline(GGsite$n.obs, col = "steelblue")
```

### Question 1b: How does urbanzation effect pollinators, herbivores, and predator abundances?

##### Running Mixed Effect Models

```{r}
#Bee abundances
pol.obs.lme2 <-glmer.nb(n.obs.pol ~ imp200m+scaled_wealth_index_2022 +(1|month), data = GGsite)
sum.pol <- summary(pol.obs.lme2)
sum.pol

backtransformed_q1_pol <- data.frame (predictor= c("imp1km", "wealthindex"),
                  anti_log_coef = c(exp(sum.pol$coefficients[2,1]),exp(sum.pol$coefficients[3,1])),
                  anti_log_lowCI = c(exp(sum.pol$coefficients[2,1]- sum.pol$coefficients[2,2]),
                  exp(sum.pol$coefficients[3,1]-sum.pol$coefficients[3,2])),
                  anti_log_highCI = c(exp(sum.pol$coefficients[2,1]+ sum.pol$coefficients[2,2]),
                    exp(sum.pol$coefficients[3,1]+sum.pol$coefficients[3,2])))                  

#Herbivore abundances
herb.obs.lme <- glmer.nb(n.obs.herb ~ imp200m + scaled_wealth_index_2022 +(1|month),data = GGsite)
sum.herb <- summary(herb.obs.lme)
sum.herb

backtransformed_q1_herb <- data.frame (predictor= c("imp1km", "wealthindex"),
                  anti_log_coef = c(exp(sum.herb$coefficients[2,1]),exp(sum.herb$coefficients[3,1])),
                  anti_log_lowCI = c(exp(sum.herb$coefficients[2,1]- sum.herb$coefficients[2,2]),
                  exp(sum.herb$coefficients[3,1]-sum.herb$coefficients[3,2])),
                  anti_log_highCI = c(exp(sum.herb$coefficients[2,1]+ sum.herb$coefficients[2,2]),
                    exp(sum.herb$coefficients[3,1]+sum.herb$coefficients[3,2])))   

#Predator abundances
pred.obs.lme <- glmer.nb(n.obs.pred ~ imp200m + scaled_wealth_index_2022+(1|month),data = GGsite)
sum.pred <- summary(pred.obs.lme)
sum.pred


backtransformed_q1_pred <- data.frame (predictor= c("imp1km", "wealthindex"),
                  anti_log_coef = c(exp(sum.pred$coefficients[2,1]),exp(sum.pred$coefficients[3,1])),
                  anti_log_lowCI = c(exp(sum.pred$coefficients[2,1]- sum.pred$coefficients[2,2]),
                  exp(sum.pred$coefficients[3,1]-sum.pred$coefficients[3,2])),
                  anti_log_highCI = c(exp(sum.pred$coefficients[2,1]+ sum.pred$coefficients[2,2]),
                    exp(sum.pred$coefficients[3,1]+sum.pred$coefficients[3,2])))

#Getting R square values

require(lme4)
require(MuMIn)
r.squaredGLMM(pol.obs.lme2)
r.squaredGLMM(herb.obs.lme)
r.squaredGLMM(pred.obs.lme)
```

##### Checking Model assumptions

```{r}
plot(pol.obs.lme2)
```

### Question 2a: How do insect abundances at a garden site impact the herbivory damage on pepper plants?

##### Running Mixed Effect Models

```{r}
#Filter for covered and uncovered peppers
GGAugust.covered <- GGAugust%>% filter(GGAugust$treatment== "covered")
GGAugust.uncovered <- GGAugust%>% filter(GGAugust$treatment== "uncovered")

## Includes all arthropods categorized as herbivore or omnivore
herbivory.lme.0 <-lmer(log_herbivory ~ n.obs.herb*treatment +(1|site), data = GGAugust)
summary(herbivory.lme.0)

herbivory.lme.1 <-lmer(log_herbivory ~ treatment +(1|site), data = GGAugust)
summary(herbivory.lme.1)
```

##### Checking Model assumptions

```{r}
#Residual plots
par(mfrow = c(1,2))
plot(herbivory.lme.0,
     main = "Fitted vs Residual Plot of Herbivory",
     adj = .75,
    cex.sub = 1)
#Looks fine
```
### Question 2b: How predator abundances at a garden site impact the herbivory damage on pepper plants?

##### Running Mixed Effect Models

```{r}
## Includes all arthropods categorized as predator in functional group category
predation.lme.1 <-lmer(log_herbivory ~ n.obs.pred +(1|site), data = GGAugust.uncovered)
summary(predation.lme.1)
```

##### Checking Model assumptions

```{r}
#Residual plots
par(mfrow = c(1,2))
plot(herbivory.lme.0,
     main = "Fitted vs Residual Plot of Herbivory",
     adj = .75,
    cex.sub = 1)
```

### Question 3:How does bee abundance and diversity at a garden site impact pepper plant fruit sizes?

*H3) As pollinator insect abundance and diversity increase, pepper plant fruit mass will increase as a result of increased pollination services.*

##### Running Mixed Effect Model

```{r}
GGAugust.uncovered$scaled_n.obs.pol <- scale(GGAugust.uncovered$n.obs.pol, center = TRUE)

#With just uncovered peppers and bee abundance and diversity
pepper.lme.1 <-lmer(log_mass_g ~ n.obs.pol + bee.simpson.x + greenhouse + (1|site), data = GGAugust.uncovered)
summary(pepper.lme.1) # bee diversity is significant

pepper.lme.c <-lmer(log_mass_g ~ n.obs.pol + bee.simpson.x + greenhouse + (1|site), data = GGAugust.covered)
summary(pepper.lme.c) #no effect of diversity or abundance for covered plants. 

pepper.lme.4 <-lmer(pepper.obs ~ n.obs.pol + bee.simpson.x + greenhouse + (1|site), data = GGAugust.uncovered)
summary(pepper.lme.4) #not signifcant effect of any covariate on pepper count
```

#### Checking Model Assumptions

```{r}
cor.test(GGAugust.uncovered$bee.simpson.x, GGAugust.uncovered$n.obs.pol)
#Bee simpson diversity and abundance are not highly correlated

plot(pepper.lme.1,
     main = "Fitted vs Residual Plot of Pepper Mass",
     adj = .75,
    cex.sub = 1)
#Looks okay
```

### Question 4: Is there a relationship between impervious surface and wealth index and bee species richness/biodiversity?

```{r}
#Bee Species Richness
#It is run with log transformed response, instead of glm because the poisson distribution wont work because it is not count data (non-integer)
beeRich.glm.1 <- lmer(log_bee.simpson ~ imp200m + scaled_wealth_index_2022 + (1|month),data = GGsite)
summary(beeRich.glm.1)
```

### Question 5: Structural Equation Modeling

*Is there an indirect effect of urbanization and wealth index on pepper plant yield?*

```{r}
#trying with Lm instead of Lmer
beerich <- lm(bee.simpson.x ~ scaled_wealth_index_2022 + imp200m +n.obs.pred, data = GGAugust.uncovered)
beeobs <- glm.nb(n.obs.pol~ scaled_wealth_index_2022 + imp200m +n.obs.pred, data = GGAugust.uncovered)
herb.abund <- glm.nb(n.obs.herb ~ scaled_wealth_index_2022 + imp200m +n.obs.pred, data = GGAugust.uncovered)
herbivory <-  lm(log_herbivory ~ n.obs.pol + bee.simpson.x + n.obs.herb +n.obs.pred+ greenhouse, data = GGAugust.uncovered)
pred.abund <- glm.nb(n.obs.pred ~ scaled_wealth_index_2022 + imp200m, data = GGAugust.uncovered)
pepperMass <- lm(log_mass_g ~ log_herbivory +n.obs.pol + bee.simpson.x + greenhouse, data = GGAugust.uncovered)

#Running piecewise model
SEMmodel <-psem(beerich,herbivory, beeobs, pepperMass,herb.abund,pred.abund, bee.simpson.x %~~% n.obs.herb, bee.simpson.x %~~% n.obs.pol, n.obs.herb %~~% n.obs.pol, n.obs.pred %~~% bee.simpson.x, data= GGAugust.uncovered)
SEMmodel

basisSet(SEMmodel)
dSep(SEMmodel, .progressBar = FALSE)
summary(SEMmodel)
```

### Question 6: Are there differences in bee community composition across sites?

*H6) Each site will differ in bee community composition and these differences will be correlated with urbanization and wealth index.*

```{r}
#Creating NMDS
set.seed(1000)
Bees.nmds <- metaMDS(BeeNMDSinput, distance = "bray", k=2) #Creating Bee NMDS

#Creating dataframe of environmental variables of interest
GGsiteAugust <- GGsite%>% filter(GGsite$month== "August")
env <-GGsiteAugust[,c(2,29,44)]

#Running envfit function
envfit.results <-envfit(Bees.nmds,env, permutations = 999, na.rm= TRUE)
     #Wealth Index is significant!
summary(envfit.results)

genus_specie <-GGspecieWide.ALL$genus_specie
#Figure out which species are driving site distribution pattern
sppfit.results <- envfit(Bees.nmds, BeeNMDSinput, permutations = 999)
sppfit.results

Bees.nmds$species

#Extracting scores from NMDS
##Site scores
data.scores <- as.data.frame(scores(Bees.nmds$points))
data.scores$site <-GGsiteAugust$site
data.scores$wealth <-GGsiteAugust$wealth_index_2022
data.scores$imp <-GGsiteAugust$imp200m
wealth.data.scores <- data.scores[,c(1,2,4)]

##Species scores
species.scores <-as.data.frame(scores(Bees.nmds$species))
species.scores$species <-GGspecieWide.ALL$genus_specie
species.scores$pvals <-sppfit.results$vectors$pvals
sig.species.scores <-subset(species.scores, pvals <=0.05)
sig.species.scores$species.clean <-c("L. dialictus spp.","B. nevadensis","M. coreopsis")

```

Model Checks

```{r}
stressplot(Bees.nmds) #Shepard Stressplot. Not too much scatter away from line= good
```


# Data Visualization

## Main Text Figures

#### Question 1

```{r}
#Arthropod abundance by impervious surface 500 m
q1a <-ggplot(data = GGsite, aes(x= imp500m, y=n.obs))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE, color = "#bf2800")+
  labs( x = "% impervious surface",
        y = "Arthropod abundance")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))
q1a
```

```{r}
#Arthropod abundance by functional groups over 200 m
q1.bee <-ggplot(data = GGsite, aes(x= imp200m, y=n.obs.pol))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE, color = "black")+
  labs( x = "",
        y = "Pollinator abundance")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 25))
q1.bee

q1.herb <-ggplot(data = GGsite, aes(x= imp200m, y=n.obs.herb))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE, color = "black")+
  labs( x = "",
        y = "Herbivore abundance")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 25))
q1.herb

q1.pred <-ggplot(data = GGsite, aes(x= imp200m, y=n.obs.pred))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE, color = "black")+
  labs( x = "% impervious surface",
        y = "Predator abundance")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 25),
  axis.title.y = element_text(size = 25))
q1.pred
```


```{r}
#Arthropod abundance by functional groups and wealth index
q1.w.bee <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs.pol))+
  geom_point(size = 3)+
  labs( x = "",
        y = "")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))
q1.w.bee

q1.w.herb <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs.herb))+
  geom_point(size = 3)+
  labs( x = "",
        y = "")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))
q1.w.herb

q1.w.pred <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs.pred))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE, color = "black")+
  labs( x = "2022 wealth index",
        y = "")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 25),
  axis.title.y = element_text(size = 20))
q1.w.pred
```


#### Question 3

```{r}
#Pepper Fruit Size Plot and Bee Abundance

#With smooth geom
q3a <-ggplot(GGAugust.uncovered, aes(x=bee.simpson.x, y=log_mass_g))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE, color = "black")+
  theme_classic()+
     labs(y = "Ln pepper mass (grams)", x = "Bee Hill-Simpson diversity")+
  scale_colour_few()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))

q3a
```


#### Question 4
```{r}
#Bee Hill-Simpson by impervious surface 500m
q1c <-ggplot(data = GGsite, aes(x= imp500m, y=log_bee.simpson))+
  geom_point(size = 3)+
  labs(x = "% impervious surface",
        y = "Ln bee Hill-Simpson diversity")+
  theme_classic()+
  scale_colour_few()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))
q1c
```


```{r}
#Bee-Simpson diversity by wealth 1 km
q1d <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=log_bee.simpson))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE, color = "#bf2800")+
    labs(x = "2022 wealth index",
        y = "Ln bee Hill-Simpson diversity")+
  theme_classic()+
  scale_colour_few()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))
q1d
```

#### Combining plots into one figure for question 1
```{r}
library(gridExtra)
library(cowplot)
q1panelfig <-ggarrange(ggarrange(q1.bee,q1.w.bee, ncol = 2, labels = c("","")),
                       ggarrange( q1.herb,q1.w.herb, ncol = 2, labels = c("","")),
                       ggarrange( q1.pred,q1.w.pred, ncol = 2, labels = c("","")), nrow = 3)
ggsave("q1.png", q1panelfig, width = 10, height = 12, units = "in")
```

#### Question 6

```{r}
NMDS.graph <-ggplot(data=data.scores) + 
  ggrepel::geom_text_repel(data = sig.species.scores, aes(x=MDS1, y=MDS2, label = species.clean), colour= "#6b6d6e", size= 5, cex = 3, direction = "both", segment.size = 0.25)+
   geom_point(aes(x=MDS1,y=MDS2, colour=wealth),size=4) +
  labs(x="NMDS1", y = "NMDS2")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 16, hjust =.75),
  axis.text.y = element_text(size = 16),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.title = element_text(size=18),
  legend.text = element_text(size=16),
  legend.position = "right",
  legend.background = element_rect(fill = "grey"))
NMDS.graph

NMDS.graph.imp <-ggplot(data=data.scores) + 
  ggrepel::geom_text_repel(data = sig.species.scores, aes(x=MDS1, y=MDS2, label = species.clean), colour= "#6b6d6e", size= 5, cex = 3, direction = "both", segment.size = 0.25)+
   geom_point(aes(x=MDS1,y=MDS2, colour=imp),size=4) +
  labs(x="NMDS1", y = "NMDS2")+
  theme_classic()+
  theme(axis.text.x = element_text(size = 16, hjust =.75),
  axis.text.y = element_text(size = 16),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.title = element_text(size=18),
  legend.text = element_text(size=16),
  legend.position = "right",
  legend.background = element_rect(fill = "grey"))
NMDS.graph.imp
```

### Supplemental Figures

Correlation between wealth index and impervious surface
```{r}
S1 <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=imp200m))+
  geom_point(size = 3)+
    labs(x = "2022 Wealth Index (1 km)",
        y = "% impervious surface (200m)")+
  theme_classic()+
  scale_colour_few()+
  theme(axis.text.x = element_text(size = 19,hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
 )
S1
```

Total arthropod abundance with month included
```{r}
#Arthropod abundance by impervious surface 500 m
S2a <-ggplot(data = GGsite, aes(x= imp200m, y=n.obs, color = month, shape = month))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE)+
  labs( x = "% impervious surface",
        y = "Total arthropod abundance",
        color  = "Month", 
        shape = "Month")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
    scale_colour_viridis_d("Month") 
S2a

S2b <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs, color = month, shape = month))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE)+
  labs( x = "2022 Wealth Index",
        y = "Total arthropod abundance",
        color  = "Month", 
        shape = "Month")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
    scale_colour_viridis_d("Month") 
S2b
```

Functional group abundances with month included (impervious surface)
```{r}
#Arthropod abundance by functional groups over 200 m
S3a.pol <-ggplot(data = GGsite, aes(x= imp200m, y=n.obs.pol,color = month, shape = month))+
  geom_point(size = 3, show.legend = FALSE)+
  geom_smooth(method = lm, se= FALSE, show.legend = FALSE)+
  labs( x = "",
        y = "Pollinator abundance")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 25))+
  scale_colour_viridis_d("Month") 
S3a.pol

S3a.herb <-ggplot(data = GGsite, aes(x= imp200m, y=n.obs.herb, color = month,shape = month))+
  geom_point(size = 3, show.legend = FALSE)+
  geom_smooth(method = lm, se= FALSE, show.legend = FALSE)+
  labs( x = "",
        y = "Herbivore abundance")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 25))+
    scale_colour_viridis_d("Month")
S3a.herb 

S3a.pred <-ggplot(data = GGsite, aes(x= imp200m, y=n.obs.pred, color = month,shape = month))+
  geom_point(size = 3, show.legend = FALSE)+
  geom_smooth(method = lm, se= FALSE, show.legend = FALSE)+
  labs( x = "% impervious surface",
        y = "Predator abundance")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 25),
  axis.title.y = element_text(size = 25))+
    scale_colour_viridis_d("Month")
S3a.pred
```
Functional group abundances with month included (wealth index)
```{r}
#Arthropod abundance by functional groups and wealth index
S3b.pol <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs.pol, color = month, shape = month))+
  geom_point(size = 3, show.legend = FALSE)+
  geom_smooth(method = lm, se= FALSE, show.legend = FALSE)+
  labs( x = "",
        y = "")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
    scale_colour_viridis_d("Month")
S3b.pol

S3b.herb <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs.herb, color = month,shape = month))+
  geom_point(size = 3, show.legend = FALSE)+
  geom_smooth(method = lm, se= FALSE, show.legend = FALSE)+
  labs( x = "",
        y = "")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))+
    scale_colour_viridis_d("Month")
S3b.herb 

S3b.pred  <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs.pred, color = month, shape = month))+
  geom_point(size = 3, show.legend = FALSE)+
  geom_smooth(method = lm, se= FALSE, show.legend = FALSE)+
  labs( x = "2022 wealth index",
        y = "")+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 25),
  axis.title.y = element_text(size = 20))+
    scale_colour_viridis_d("Month")
S3b.pred
```

Compiled into one figure

```{r}
Supp3panelfig <-ggarrange(ggarrange(S3a.pol,S3b.pol, ncol = 2, labels = c("","")),
                       ggarrange(S3a.herb,S3b.herb, ncol = 2, labels = c("","")),
                       ggarrange(S3a.pred,S3b.pred, ncol = 2, labels = c("","")), nrow = 3)

ggsave("Supp3.png", Supp3panelfig, width = 10, height = 12, units = "in")
```
Plot just to extract legend
```{r}

S3b.pred.legend  <-ggplot(data = GGsite, aes(x= wealth_index_2022, y=n.obs.pred, color = month, linetype = month, shape = month))+
  geom_point(size = 3)+
  geom_smooth(method = lm, se= FALSE)+
  labs( x = "2022 wealth index",
        y = "",
        color  = "Month", 
        linetype = "Month", 
        shape = "Month")+
        scale_linetype_manual(values = c(3,2,1))+
  scale_shape_manual(values = c(1,10,16))+
  theme_classic()+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 25),
  axis.title.y = element_text(size = 20),
  legend.key.size = unit(1, 'cm'),
  legend.title = element_text(size=14),
   legend.text = element_text(size=12))+
    scale_colour_viridis_d("Month")
S3b.pred.legend
```

Wealth correlation plot
```{r}
income <- ggplot(GGsite, aes(x =med_houseincome_2022, y = wealth_index_2022))+
  geom_point()+
  geom_smooth(method = lm, color = "#050524")+
  theme_classic()+
  labs(x= "Median household income", y = "Wealth Index" )+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))

networth <- ggplot(GGsite, aes(x =med_networth_2022, y = wealth_index_2022))+
  geom_point()+
  geom_smooth(method = lm, color = "#050524")+
  theme_classic()+
  labs(x= "Median networth", y = "Wealth Index" )+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))

homevalue <- ggplot(GGsite, aes(x =med_homevalue_2022, y = wealth_index_2022))+
  geom_point()+
  geom_smooth(method = lm, color = "#050524")+
  theme_classic()+
  labs(x= "Median home value", y = "Wealth Index" )+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))

renters <- ggplot(GGsite, aes(x =renter_occ_Hus_2022, y = wealth_index_2022))+
  geom_point()+
  geom_smooth(method = lm, color = "#050524")+
  theme_classic()+
  labs(x= "Renter occupied housing", y = "Wealth Index" )+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))

Supp4panelfig <-ggarrange(ggarrange(income),
                        ggarrange(renters),  
                       ggarrange(networth),
                       ggarrange(homevalue), ncol = 2, nrow = 2)

ggsave("Supp4.png", Supp4panelfig, width = 12, height = 8, units = "in")
```


Log likelihoods for impervious surface scale
```{r}
#Creating Vectors for log likelihoods
x1 <-glmer.nb(n.obs ~ imp200m +scaled_wealth_index_2022 + (1|month), data = GGsite)
x2 <-glmer.nb(n.obs ~ imp500m+scaled_wealth_index_2022 + (1|month), data = GGsite)
x3 <-glmer.nb(n.obs ~ imp1km+scaled_wealth_index_2022 + (1|month), data = GGsite)
x4 <-glmer.nb(n.obs ~ imp1.5km+scaled_wealth_index_2022  + (1|month), data = GGsite)
x5 <-glmer.nb(n.obs ~ imp2km+scaled_wealth_index_2022  + (1|month), data = GGsite)
likelihood.test <-c(x2,x3,x4,x5)

#Running Log Likelihoods
ll1 <-logLik(x1, REML =FALSE)
ll2 <-logLik(x2, REML =FALSE)
ll3 <-logLik(x3, REML =FALSE)
ll4 <-logLik(x4, REML =FALSE)
ll5 <-logLik(x5, REML =FALSE)

likelihood.test <-data.frame("likelihood" = c(ll1,ll2,ll3,ll4,ll5), 
                                "scale" = c(200,500,1000,1500,2000))
#Creating a Theme
My_Theme = theme(
  axis.title.x = element_text(size = 14),
  axis.text.x = element_text(size = 11),
  axis.text.y = element_text(size = 11),
  axis.title.y = element_text(size = 14),
  plot.title = element_text(size = 16))

#Plotting Log Likelihoods
ggplot(likelihood.test, aes(x = scale, y = likelihood))+
  geom_smooth(color = "#050524")+
  theme_classic()+
  labs(x= "% impervious surface scale (m)", y = "Log likelihood" )+
  theme(axis.text.x = element_text(size = 19, hjust =.75),
  axis.text.y = element_text(size = 19),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20))
## Shows that 500 m is the best scale
```


### Software and Package Versions for Report
```{r}
report_packages()
citation()
```
